An Invariant Framework for Conducting Reproducible Computational Science

### 2015-01-14 paper.tex
Acks

\input {intro}
\input {tauroast}
\input {observation}
\input {evolution}
\input {measure}
\input {evaluation}
\input {problems}
\input {related_work}
\input {postscript}

@@

This work was supported in part by National Science Foundation grants PHY-1247316 (DASPOS), 
OCI-1148330 (SI2) and PHY-1312842.
The University of Notre Dame Center for Research Computing scientists and engineers provided critical technical assistance throughout this research effort.

Copyright (C) 2014 The University of Notre Dame

This work is licensed under the Creative Commons Attribution 4.0 License.

>>>>

\input {intro}
\input {tauroast}
\input {observation}
\input {evolution}
%\input {measure}
\input {evaluation}
\input {problems}
\input {related_work}
%\input {postscript}

@@

This work was supported in part by National Science Foundation grants PHY-1247316 (DASPOS), 
OCI-1148330 (SI2), PHY-1312842, ICER-1440327, SES-0951576 (RDCEP), and ICER-1343816 (UChicago subcontract).
The University of Notre Dame Center for Research Computing scientists and engineers provided critical technical assistance throughout this research effort.
The Open Science Grid at the University of Chicago provided critical technical assistance throughout this research effort.
